Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-06-10 analysis/paper/paper.Rmd
adding comments to rmd

@@

For us to easily discuss the topic, we first must define what we mean so that we may clearly communicate.
Many of the terms used in this area have varying definitions that may or may not agree with each other.
For instance, reproducible research is recently highlighted by many authors [@Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue.
The International Union of Pure and Applied Chemistry provides definitions of repeatability in the "Compendium of Chemical Terminology -- Gold Book" as:

@@

@@

@@

We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely subjective.
We have based our scoring decisions on our own experiences in the field of plant pathology.
While many software packages may be widely used or "freely" available if one has an institutional licence, these types of software often hinder partners and interested parties that do not have these luxuries.
Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.

@@

The fourth level includes packaging the analysis as a software package, *e.g.*, R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al. [@Khaliq2020] have done.
Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conida dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al. used [-@Miorini2018, -@Miorini2019].
Kamvar et al. [-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most ouptut files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.

>>>>

<!--# not sure we need a separate section for definitions, but presence continuously in the text -->

@@

For us to easily discuss the topic, we first must define what we mean so that we may clearly communicate.
Many of the terms used in this area have varying definitions that may or may not agree with each other.
For instance, reproducible research is recently highlighted by many authors [@Baker2016a; @Iqbal2016; @Nature2016; @Patil2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013; ]

<!--# These references above are all prior 2017. We may want to update the list? -->

as an important issue.
The International Union of Pure and Applied Chemistry provides definitions of repeatability in the "Compendium of Chemical Terminology -- Gold Book" as:

@@

<!--# I would simplify and just mention the Peng's definition as most appropriate for our context -->

@@

<!--# I am leaning towards a sytle that shows the methods at the end in a separate section? -->

@@

We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely subjective.
We have based our scoring decisions on our own experiences in the field of plant pathology.
While many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have these luxuries.
Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.

@@

The fourth level includes packaging the analysis as a software package, *e.g.*, R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al. [@Khaliq2020] have done.
Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conida dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al. used [-@Miorini2018, [-@Miorini2019]].
Kamvar et al. [-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most ouptut files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.
